### 2016-09-08 Theorem3_FP.tex
Proof3

\acnote{INCOMPLETE. To be verified before moving the theorem to section 4}
\heading{Classical Bloom filter in random oracle model (ROM). }
Fix $n,k,m \geq 0$ and let $\mathcal{S}=[\univ]^n$.  Then $\Pi_{\mathrm{Bloom}}= (\calQ,\Rep, \Qry)$ is defined as in Figure~\ref{fig:bf-and-garbled-bf} (left side).  The following result shows,
\begin{theorem}\label{thm3}
Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{Bloom}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure just described. For any adversary~$A$ that makes a total of~$q$ queries to the oracle and has time-complexity~$O(t)$, there exist prf-adversaries~$B_1,B_2$ (explicitly constructed in the proof of this theorem) such that
\[
\AdvCorrect{\Pi_{\mathrm{Bloom}},\distr{\calS}{},r}{A} \leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  +{\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
\]
\end{theorem}

\begin{proof}[\Cref{thm3}]
We use a game playing argument to prove this theorem in the ROM. In $\game{0}$, the $\HashOracle$ does lazy sampling of elements from $[m]$ to mimic a random oracle(RO). For every distinct query, $\Hash$ returns a random value sampled from $[m]$. Here, the adversary $A$, along with $\Rep$ and $\Qry$ are given access to $\Hash$. It can be seen that, $\game{0}$ exactly simulates the correctness game of $\Pi_{\mathrm{Bloom}}$. So, $\AdvCorrect{\Pi_{\mathrm{Bloom}},\distr{\calS}{},r}{A} = \Prob{\game{0}(A) = 1}$.

\begin{figure}
\fpage{.9}{
\hpagessl{.45}{.5}
{
\underline{\game{0}(A)}\\
$S \getsr \distr{\calS}{}$, $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$z \getsr A^{\TestOracle, \HashOracle}(S,\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\
%
\oracle{$\TestOracle(q_x)$}\\
$a \gets \Qry^{\HashOracle}(\pubaux,\privaux,q_x)$\\
if $a \neq q_x(S)$ then \\
\nudge $\err \gets\err +1$\\
Return~$(a,\err )$\\
%
\oracle{$\HashOracle(i,q_y)$}\\
$v \getsr [m]$\\
if $T[i,q_y] \neq \undefined$\\
\nudge $v \gets T[i,q_y]$\\
$T[i,q_y] \gets v$\\
Ret $v$
}
{
\underline{$\game{1}(A)$}\\
$S \getsr \distr{\calS}{}$, $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$z \getsr A^{\TestOracle, \HashOracle}(S,\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\ 
%
\oracle{$\TestOracle(q_x)$}\\
$M \gets\pubaux$\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge $h_j \gets \HashOracle(j,q_x)$\\
\nudge if $M[h_j] \neq 1$ then Return $(0, \err)$\\
$\err \gets \err +1$\\
Return~$(1,\err )$\\
%
\oracle{$\HashOracle(i,q_y)$}\\
$v \getsr [m]$\\
if $T[i,q_y] \neq \undefined$\\
\nudge $v \gets T[i,q_y]$\\
$T[i,q_y] \gets v$\\
Ret $v$
}
}
\fpage{.9}{
\hpagessl{.45}{.5}
{
\underline{$\game{2}(A)$}\\
$S \getsr \distr{\calS}{}$, $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$z \getsr A^{\TestOracle, \HashOracle}(S,\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\ 
%
\oracle{$\TestOracle(q_x)$}\\
$M \gets\pubaux$\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge $h_j \gets \HashOracle(j,q_x)$\\
\nudge if $M[h_j] \neq 1$\\
\nudge \nudge if $j = 1$ then Return $(0, \err, \emptystring)$\\
\nudge \nudge Return $(0, \err, (h_1, \ldots, h_{j-1}))$\\
$\err \gets \err +1$\\
Return~$(1,\err, (h_1, \ldots, h_{k}) )$\\
%
\oracle{$\HashOracle(i,q_y)$}\\
$v \getsr [m]$\\
if $T[i,q_y] \neq \undefined$\\
\nudge $v \gets T[i,q_y]$\\
$T[i,q_y] \gets v$\\
Ret $v$
}
{
\underline{$\game{3}(A)$}\\
$S \getsr \distr{\calS}{}$, $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$z \getsr A^{\TestOracle, \HashOracle}(S,\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\ 
%
\oracle{$\TestOracle(q_x)$}\\
$M \gets\pubaux $\\
$(h_1, \ldots, h_{k}) \gets \HashOracle(q_x)$\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge if $M[h_j] \neq 1$ then \\
\nudge \nudge Return~$(0,\err, (h_1, \ldots, h_{k}) )$\\
$\err \gets \err +1$\\
Return~$(1,\err, (h_1, \ldots, h_{k}) )$\\
%
\oracle{$\HashOracle(q_y)$}\\
$v_j \getsr [m]$\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge if $T[j,q_y] \neq \undefined$\\
\nudge \nudge $v_j \gets T[j,q_y]$\\
\nudge $T[j,q_y] \gets v_j$\\
Ret $\left(v_1,\ldots,v_k\right)$
}
}
\caption{\Cref{thm3}: Game playing argument}\label{fig:3TGame}
\end{figure}
\begin{figure}
\fpage{.9}{
\hpagessl{.45}{.5}
{
\underline{\game{4}(A)\fbox{\game{5}(A)}}\\
$S \getsr \distr{\calS}{}$\\
$\err \gets 0$, $\Ans \gets \emptyset$\\
$c \gets 0$, $\bad \gets \false$\\
$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$z \getsr A^{\TestOracle, \HashOracle}(S,\pubaux)$\\
if $\bad = \true$ then \fbox{Return 0}\\
if $\err  < r$ then Return 0\\
Return 1\\
%
\oracle{$\TestOracle(q_x)$}\\
if $\Ans[x] \neq \undefined$\\
\nudge $(h_1, \ldots, h_{k}) \gets \HashOracle(q_x)$\\
Return $\Ans[x]$\\
%
}
{
\oracle{$\HashOracle(q_y)$}\\
$c \gets c + 1$\\
$v_j \getsr [m]$\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge if $T[j,x] \neq \undefined$\\
\nudge \nudge $v_j \gets T[j,q_y]$\\
\nudge $T[j,q_y] \gets h_j$\\
%
$M \gets\pubaux$\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge if $M[v_j] \neq 1$ then \\
\nudge \nudge $\Ans[q_y] \gets (0,\err, (v_1, \ldots, v_{k}) )$\\
\nudge \nudge if $c \in \calI$ then $\bad \gets \true$\\
\nudge \nudge $\Break$\\
if $c \notin \calI$ then $\bad \gets \true$\\
$\err \gets \err +1$\\
$\Ans[q_y] \gets (0,\err, (v_1, \ldots, v_{k}))$\\
Ret $\left(v_1,\ldots,v_k\right)$
}
}
\caption{\Cref{thm3}: Game playing argument}\label{fig:3TGame}
\end{figure}

>>>>

\heading{Classical Bloom filter in random oracle model (ROM). }
Fix $n,k,m \geq 0$ and let $\mathcal{S}=[\univ]^n$.  Then $\Pi_{\mathrm{Bloom}}= (\calQ,\Rep, \Qry)$ is defined as in Figure~\ref{fig:bf-and-garbled-bf} (left side).  The following result shows,
\begin{theorem}\label{thm3}
Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{Bloom}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure just described. For any adversary~$A$ that makes a total of~$q_T$ queries to the $\Test$ oracle, and $q_R$ queries to the RO, and has time-complexity~$O(t)$, then
\[
\AdvCorrect{\Pi_{\mathrm{Bloom}},\distr{\calS}{},r}{A} \leq  {\dbinom{q_T + q_H}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
\]
\end{theorem}

\begin{proof}[\Cref{thm3}]
We use a game playing argument to prove this theorem in the ROM. In $\game{0}$, the $\Hash$ does lazy sampling of elements from $[m]$ to mimic a random oracle(RO). For every distinct query, $\Hash$ returns a random value sampled from $[m]$. Here, the adversary $A$, along with $\Rep$ and $\Qry$ are given access to $\Hash$. It can be seen that, $\game{0}$ exactly simulates the correctness game of $\Pi_{\mathrm{Bloom}}$. So, $\AdvCorrect{\Pi_{\mathrm{Bloom}},\distr{\calS}{},r}{A} = \Prob{\game{0}(A) = 1}$.

$\game{1}$ is exactly same as $\game{0}$ except the $\Qry$ oracle is replaced by the code of $\Qry$, whereas in $\game{2}$, the $\Test$ oracle returns the hash values back to the adversary along with value of $\err$ and output of the $\Qry$ oracle. $\game{3}$ on the other hand, returns all the $k$ hash values for any query. This results in adversary getting $(k-1)$ hash values for free corresponding to each query, whereas we charge the adversary for a single query. Since $k$ is likely to be very small compared to the number of queries the adversary makes, this does not change the dynamics significantly. Also, in real world, RO will be a hash function, and hence the adversary can perform local computations to get the hash values. It can be easily seen that the output of all the games will be same. Hence, $\Prob{\game{0}(A) = 1} = \Prob{\game{1}(A) = 1} = \Prob{\game{2}(A) = 1} = \Prob{\game{3}(A) = 1}$.

In $\game{4}$, we offload all of $\Test$'s computations to $\Hash$, which now maintains an $\Ans$ table to compute and save answers for each query. For any query, $q$, the $\Test$ oracle returns answer stored at $\Ans[q]$. We also introduce the $\bad$ flag in this game. Like in the earlier proofs,  $\bad$ is set to true, if queries indexed by the r-set $\calI$ fail to be false positives, or the other queries are false-positives. $\bad$ in fact does not affect the output of $\Hash$ or the game. So, $\Prob{\game{4}(A) = 1} = \Prob{\game{3}(A) = 1}$. $\game{5}$ is exactly same as $\game{4}$, but returns 0, if $\bad$ is set to true. It can be observed that, the total queries made to the $\Hash$ oracle by the adversary(in both games) is the sum of queries($q_T$) made by the $\Test$ oracle, and adversary's direct queries($q_H$). Using analyses and intermediate results of previous proofs, $\Prob{\game{5}(A)=1} = \frac{1}{\dbinom{q}{r}}\Prob{\game{4}(A)=1}$.

To summarize, 
\[
\AdvCorrect{\Pi_{\mathrm{Bloom}},\distr{\calS}{},r}{A} \leq  {\dbinom{q_T + q_H}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
\]
which is the bound claimed in the theorem statement.
\begin{figure}
\fpage{.9}{
\hpagessl{.45}{.5}
{
\underline{\game{0}(A)}\\
$S \getsr \distr{\calS}{}$, $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$z \getsr A^{\TestOracle, \HashOracle}(S,\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\
%
\oracle{$\TestOracle(q_x)$}\\
$a \gets \Qry^{\HashOracle}(\pubaux,\privaux,q_x)$\\
if $a \neq q_x(S)$ then \\
\nudge $\err \gets\err +1$\\
Return~$(a,\err )$\\
%
\oracle{$\HashOracle(i,q_y)$}\\
$v \getsr [m]$\\
if $T[i,q_y] \neq \undefined$\\
\nudge $v \gets T[i,q_y]$\\
$T[i,q_y] \gets v$\\
Ret $v$
}
{
\underline{$\game{1}(A)$}\\
$S \getsr \distr{\calS}{}$, $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$z \getsr A^{\TestOracle, \HashOracle}(S,\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\ 
%
\oracle{$\TestOracle(q_x)$}\\
$M \gets\pubaux$\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge $h_j \gets \HashOracle(j,q_x)$\\
\nudge if $M[h_j] \neq 1$ then Return $(0, \err)$\\
$\err \gets \err +1$\\
Return~$(1,\err )$\\
%
\oracle{$\HashOracle(i,q_y)$}\\
$v \getsr [m]$\\
if $T[i,q_y] \neq \undefined$\\
\nudge $v \gets T[i,q_y]$\\
$T[i,q_y] \gets v$\\
Ret $v$
}
}
\fpage{.9}{
\hpagessl{.45}{.5}
{
\underline{$\game{2}(A)$}\\
$S \getsr \distr{\calS}{}$, $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$z \getsr A^{\TestOracle, \HashOracle}(S,\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\ 
%
\oracle{$\TestOracle(q_x)$}\\
$M \gets\pubaux$\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge $h_j \gets \HashOracle(j,q_x)$\\
\nudge if $M[h_j] \neq 1$\\
\nudge \nudge if $j = 1$ then Return $(0, \err, \emptystring)$\\
\nudge \nudge Return $(0, \err, (h_1, \ldots, h_j))$\\
$\err \gets \err +1$\\
Return~$(1,\err, (h_1, \ldots, h_{k}) )$\\
%
\oracle{$\HashOracle(i,q_y)$}\\
$v \getsr [m]$\\
if $T[i,q_y] \neq \undefined$\\
\nudge $v \gets T[i,q_y]$\\
$T[i,q_y] \gets v$\\
Ret $v$
}
{
\underline{$\game{3}(A)$}\\
$S \getsr \distr{\calS}{}$, $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$z \getsr A^{\TestOracle, \HashOracle}(S,\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\ 
%
\oracle{$\TestOracle(q_x)$}\\
$M \gets\pubaux $\\
$(h_1, \ldots, h_{k}) \gets \HashOracle(q_x)$\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge if $M[h_j] \neq 1$ then \\
\nudge \nudge Return~$(0,\err, (h_1, \ldots, h_{k}) )$\\
$\err \gets \err +1$\\
Return~$(1,\err, (h_1, \ldots, h_{k}) )$\\
%
\oracle{$\HashOracle(q_y)$}\\
$v_j \getsr [m]$\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge if $T[j,q_y] \neq \undefined$\\
\nudge \nudge $v_j \gets T[j,q_y]$\\
\nudge $T[j,q_y] \gets v_j$\\
Ret $\left(v_1,\ldots,v_k\right)$
}
}
\caption{\Cref{thm3}: Game playing argument}\label{fig:3TGame}
\end{figure}
\begin{figure}
\fpage{.9}{
\hpagessl{.45}{.5}
{
\underline{\game{4}(A)\fbox{\game{5}(A)}}\\
$S \getsr \distr{\calS}{}$\\
$\err \gets 0$, $\Ans \gets \emptyset$\\
$c \gets 0$, $\bad \gets \false$\\
$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$z \getsr A^{\TestOracle, \HashOracle}(S,\pubaux)$\\
if $\bad = \true$ then \fbox{Return 0}\\
if $\err  < r$ then Return 0\\
Return 1\\
%
\oracle{$\TestOracle(q_x)$}\\
if $\Ans[x] \neq \undefined$\\
\nudge $(h_1, \ldots, h_{k}) \gets \HashOracle(q_x)$\\
Return $\Ans[x]$\\
%
}
{
\oracle{$\HashOracle(q_y)$}\\
$c \gets c + 1$\\
$v_j \getsr [m]$\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge if $T[j,x] \neq \undefined$\\
\nudge \nudge $v_j \gets T[j,q_y]$\\
\nudge $T[j,q_y] \gets v_j$\\
%
$M \gets\pubaux$\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge if $M[v_j] \neq 1$ then \\
\nudge \nudge $\Ans[q_y] \gets (0,\err, (v_1, \ldots, v_{k}) )$\\
\nudge \nudge if $c \in \calI$ then $\bad \gets \true$\\
\nudge \nudge $\Break$\\
if $c \notin \calI$ then $\bad \gets \true$\\
$\err \gets \err +1$\\
$\Ans[q_y] \gets (1,\err, (v_1, \ldots, v_{k}))$\\
Ret $\left(v_1,\ldots,v_k\right)$
}
}
\caption{\Cref{thm3}: $\game{4}$ and $\game{5}$ of game playing argument}\label{fig:3TGame}
\end{figure}
